The imprint of global magma oceans on exoplanet demographics

### 2022-08-29 src/tex/ms.tex
introduce star and planet samples

    We further define the solar-equivalent semi-major axis $a_{eff} = a (L_\star/L_\odot)^{-1/2}$, at which a planet experiences the same insolation as a Solar System planet at an orbital distance $a$.
\end{note}

@@

\subsection{Synthetic star and planet sample}
\subsubsection{Stellar sample from Gaia DR3}
\todo{Which star sample was actually used?}

\subsubsection{Planetary sample from SAG~13}
\todo[inline]{What is the source of our occurrence rate density from which we draw? We could also use a generative model that directly approximates an observed or theoretical density \citep[e.g.,][]{Schlecker2021b}.}
\begin{note}
    The NASA Exoplanet Program Analysis Group chartered Science Analysis Group 13 (SAG 13)...
    The inferred occurrence rate density can be expressed as a power law in planet radius and period
    \begin{equation}
        \frac{\partial^2n}{\partial \log R \, \partial \log P} = \Gamma R^{\alpha} P^{\beta}
    \end{equation}
that is broken in planet radius, resulting in the free parameters $\Gamma$, $\alpha$, $\beta$, and a breakpoint radius $R_\mathrm{break}$.
\end{note}

@@

>>>>

    We further define the solar-equivalent semi-major axis $a_{eff} = a (L_\star/L_\odot)^{-1/2}$, at which a planet experiences the same insolation as a Solar System planet at an orbital distance~$a$.
\end{note}

@@

\subsection{Synthetic star and planet sample}
\begin{note}
    The first step in our analysis is to generate a synthetic sample of stars and planets.
    First, we create a stellar population based on the observed population in the solar neighborhood, to which we then assign planetary systems based on occurrence rates derived from the \kepler mission.
    In our fiducial model setup, we consider stars with a maximum distance to the solar system of \dmax.
\end{note}

\subsubsection{Stellar sample from Gaia DR3}
\todo{Which star sample was actually used?}

\subsubsection{Planetary ocurrence rates in orbital period and radius}
\todo[inline]{What is the source of our occurrence rate density from which we draw? We could also use a generative model that directly approximates an observed or theoretical density \citep[e.g.,][]{Schlecker2021b}.}
\begin{note}
    The NASA Exoplanet Program Analysis Group chartered Science Analysis Group 13 (SAG 13)...
    The inferred occurrence rate density can be expressed as a power law in planet radius and period
    \begin{equation}
        \frac{\partial^2n}{\partial \log R \, \partial \log P} = \Gamma R^{\alpha} P^{\beta}
    \end{equation}
that is broken in planet radius, resulting in the free parameters $\Gamma$, $\alpha$, $\beta$, and a breakpoint radius $R_\mathrm{break}$.
\end{note}

\subsubsection{Transit probability}
\todo[inline]{describe how we model inclinations and transits of synthetic planets}
\begin{note}
    Not all planets are transiting from our point of view.
    We model the occurrence of transits by assuming random, isotropic orientations of planetary orbits and calculating the transit impact parameter $b = \cos(i)/R_\star$ for each planet.
    Only planets with $|b| < 1$ are transiting and further considered.
    For these cases we calculate the transit depth
    \begin{equation}\label{eq:transitdepth}
        \delta = \left( \frac{R_\mathrm{P}}{R_\star} \right)^2
    \end{equation}\todo[inline]{check if transit depth or duration are actually used further down}
    and transit duration
    \begin{equation}\label{eq:transitduration}
        t_{\mathrm{T}} = \frac{R_\star P}{\pi a} \sqrt{1 - b^2},
    \end{equation}
    which are relevant for the detection probability of the respective planet~(see Sect.~\ref{sec:sensitivity}).
    After excluding all non-transiting planets, the size of our nominal sample of potentially observable planets drops to $N = \Nplanets$.
\end{note}

@@

\begin{note}
\todo[inline]{Transition to tests of the trend:}
Figure~\ref{fig:has_magmaocean} shows that the subpopulation of planets with magma oceans is apparent in the synthetic dataset.
    In the following, we test if and under what conditions this effect is large enough to be detected with high significance.
\end{note}
